\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-05 paper/eccv2020/sections/hardware.tex
merging
Updated figures and discussion.

@@

\edit{To verify that our simulated diffused SPAD measurements match measurements produced by an actual diffused SPAD, we set up a system consisting of a diffused and scanned SPAD side-by-side. Details about this system can be found in the supplement. We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from the scanned SPAD are shown alongside the diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems produce near equivalent measurements. Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions. That is, they observe scene from slightly different perspectives.
}

>>>>

\begin{figure}[t]
	\centering
  \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
  \caption{Diffused SPAD results captured at $\sim$25mW laser power indoors.
    The resulting corrected depth maps from both scanning and summing transient measurements and diffusing
    the laser illumination are very similar qualitatively and quantitatively.}
  \label{fig:captured_diffuse_small}
  % \vspace{-0.5em}
\end{figure}

@@

\edit{To verify that our simulated diffused SPAD measurements match measurements
  produced by an actual diffused SPAD, we set up a system consisting of a
  diffused and scanned SPAD side-by-side. Details about this system can be found
  in the supplement. We then captured measurements of the simple scene shown in
  Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from
  the scanned SPAD are shown alongside the diffused SPAD's measurements in
  Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems
  produce near equivalent measurements. Slight differences in their two
  histograms can be attributed to a baseline difference of about 10cm between
  the SPAD positions. That is, they observe scene from slightly different
  perspectives.NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?}
\edit{We show proof-of-concept results captured by this system in
  Figure~\ref{fig:captured_diffuse_small}. For}

### 2020-03-05 paper/eccv2020/supplement.tex
Updated figures and discussion.

\section{Pseudocode, pixel shifting, and dither artifacts}
We give pseudocode for our algorithm here. In the first part of our algorithm we
compute the pixel shifting matrix mapping the histogram $h_s$ (computed from the
initial depth map and reflectance estimate)to $h_t$ (computed from the captured
transient).
{ \footnotesize
\begin{algorithm}
 \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
 \label{alg:ehm}
 \begin{algorithmic}
	\footnotesize
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
}

@@

@@

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms or error over the initial depth estimate. The
normalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the baseline between the
positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).

@@

\begin{table}[ht!]
    \renewcommand{\arraystretch}{1.3}
    \setlength{\tabcolsep}{10pt}
     \centering
     \begin{tabular}{lccc} \toprule
         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
         \textbf{Scanned} & XXX & $6\times10^7$ & XXX \\
         \textbf{Diffused} & XXX & $6\times10^7$ & XXX \\
        \bottomrule
    \end{tabular}
    \vspace{0.4em}
    \caption{\textbf{Recorded photons for diffused vs. scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
    \label{tab:photon_counts}
\end{table}

>>>>

\section{Pseudocode, pixel shifting, and dither artifacts}
We give pseudocode for our algorithm here. In the first part of our algorithm we
compute the pixel shifting matrix mapping the histogram $h_s$ (computed from the
initial depth map and reflectance estimate)to $h_t$ (computed from the captured
transient).
{ \footnotesize
\begin{algorithm}
 \caption{Find Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
	\footnotesize
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
}

@@

\section{Nominal values for SBR calculation}
Here we give the values used in the equation for received power, repeated here
for convenience:
  \begin{equation}
    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
  \end{equation}
The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c|c}
    \toprule
    Symbol & Description & Nominal Value \\
    \midrule
    $\rho$  & Albedo of lambertian surface & $0.3$ \\
    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
    $R$ & Distance to surface (m) & $3$ \\
    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
    $\eta$ & Quantum efficiency of detector & $0.3$ \\
    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
    \bottomrule
  \end{tabular}
  \caption{}
  \label{fig:sbr_calculation}
\end{figure}
Once $P_R$ is determined, we compute the number of photons using the laser
wavelength $\lambda = 532$ nm as
\begin{equation}
  N = \frac{P_R\lambda}{hc}
\end{equation}
where $h \approx 6.626 \tiems 10^{-34}$ is Planck's constant and $c \approx 3
\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
MHz, we get the number of photons per pulse as $0.043$, which puts us in the
low-flux regime.

@@

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms or error over the initial depth estimate. The
unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the baseline between the
positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).
\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
  \caption{Comparing Scan + Sum and Diffused SPAD. The transients shown are
    equal-time (and thus equal energy), and display qualitative similarity in
    the absence of pileup.}
  \label{fig:comparison}
\end{figure}

@@

\begin{table}[ht!]
    \renewcommand{\arraystretch}{1.3}
    \setlength{\tabcolsep}{10pt}
     \centering
     \begin{tabular}{lccc} \toprule
         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
         \textbf{Scanned} & $1.4\times10^7$ & $6\times10^8$ & $2.3\%$ \\
         \textbf{Diffused} & $2.4\times10^7$ & $6\times10^8$ & $4.0\%$ \\
        \bottomrule
    \end{tabular}
    \vspace{0.4em}
    \caption{\textbf{Recorded photons for diffused vs. scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
    \label{tab:photon_counts}
\end{table}
